Robotic Grasping in Clutter: Using a Hierarchy of Supervisors with Learning from Demonstrations

### 2016-03-19 paper.tex
added stuff

\begin{abstract}
Recent progress in learning from demonstrations increasingly indicates that robots can acquire manipulation skills from
large collections of training data. Online learning from demonstration algorithms such as DAgger can in particular learn
policies for problems where the system dynamics and the cost function are unknown. Traditionally, these systems have
been trained by skilled human supervisors providing feedback on the current learned policy. As the number of
demonstrations increases, this approach can however incur a substantial time and labor cost. We propose that a hierarchy of supervisors that vary is expertise but also in cost can help alleviate this issue. We combine planning on a relaxed problem with crowdsourcing and with robotics experts, and hypothesize that leveraging this combination can lead to similar performance while substantially decreasing cost. We focus on the grasping in clutter problem, and use an architecture for learning from demonstration based on DAgger and deep learning to learn policies directly from image input. Our results ....[fill in]

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{f_figs/teaser.eps}
\caption{
Three roll-outs on a Zymark 3-DOF Robot of a fully trained grasping in clutter policy (one per column, bottom to top) which was trained using a
hierarchy of three supervisors consisting of an analytical motion planning, crowd-sourcing and human expert. 
Red shapes indicate clutter objects and the robot is trained to reach the yellow circle. The trained manipulation policy is represented as a deep neural network that recieves as input an image of the scene and outputs a change in state position. The resulting policy learns to sweep away clutter objects and reach the goal object. }
\vspace*{-20pt}
\label{fig:teaser}
\end{figure}

@@

\section{Robot Grasping in Clutter}
Let us now describe how we apply the above approach for the grasping in clutter problem. We consider a robot grasping an
object in a cluttered environment. The robot's goal is to grasp a yellow cylindrical target object while other extruded
planar objects obstruct the path towards the goal object. Since contact dynamics are difficult to model \cite{kitaevphysics,kingnonprehensile}, we do not assume the knowledte of explicit object or dynamics models and instead learn a grasping policy directly from labelled
overhead video data. The state space space $\mathcal{X}$, is hence given by an image from an overhead video
camera, observing a set of K objects, the robot arm and a goal object in a bounded workspace. As the underlying reward
function, or $r: \mathcal{X}\times \mathcal{U} \rightarrow \lbrace 0, 1\rbrace$, where $U$ denotes continuous control
signals given by delta values of joint angles. We consider the following three supervisors $S_1, S_2, S_3$.

\noindent \textbf{Algorithmic Supervisor (AS)} Our first supervisor, $S_1$, is a first order motion planner that that computes
control signals for the robot to reach the goal object in a straight line, ignoring the presence of obstacles. Our
method employs template matching to identify the goal object in the image and uses the forward dynamics of the robot to
computes the relative change in direction the robot should apply as a control. The template matching is implemented in
OpenCV and uses the normalized cross-correlation filter~\cite{opencv_library}. This supervisor is intentionally
simplistic to execute and implement, and is designed to just provide an initial improvement of a random neural network policy.
We assign a cost of $C_1 = \$0.01$ to this supervisor.
\begin{figure}[t]
\centering

@@

\noindent \textbf{CrowdSourced Supervisor} The second supervisor, $S_2$, relies on a crowd source service, called Amazon
Mechanical Turk (AMT). The AMT platform makes readily available thousands of human workers that we can query to provide robot
supervision examples for approximately \$0.1 per robot trial. 
We designed the supervision interface shown in Fig. \ref{fig:overlays}. The interface displays a video of a roll-out of
the current robot policy and allows the human supervisors to command an overlay visualization of the robot arm to
showcase a deviation to the current policy that should be applied with a maximal angle joint deviation of 15 degree to
the current roll-out.

@@

\section{Experiments} \label{sec:Exp}
\begin{figure}[t]
\centering

@@

\caption{\footnotesize  The different measures of performance used in our scoring metric for how well the robot performed.  Not  Contact corresponds to when the gripper is never in contact with yellow circle. Contact corresponds to when the robot ends with the gripper in contact with yellow circle. Grasped is defined as when the yellow circle is inside the gripper. }
\vspace*{-20pt}
\label{fig:suc_meas}
\end{figure}

@@

\subsection{Experimental Setup}
We work with a Zymark robot to perform a grasping in clutter task. The robot, shown in Fig. \ref{fig:robot}, has a 3 dimensional internal state of base rotation, arm extension and gripper. The robot is commanded via state position requests, which are tracked by a tuned PID controller. We used
relative state control because this enabled us to easily enforce stay out zones (such as where a human operator might
be) to register state controlsignals to the labeling interface in Fig. \ref{fig:overlays}. We utilize the two main rotational joints of the
robot as degrees of freedom which are controled by a neural network policy $\pi_{\theta}$ trained on image data taken by
an overhead Logitech C270 camera. Examples of images from the camera can be seen in Fig. \ref{fig:teaser}.

We consider objects made of Medium Density Fiberboard with an average 4" diameter. The objects used to form clutter are
painted Red while the goal object is a yellow cylinder. The robot workspace consists of a disk region which is
surrounded by an elevated plate constraining the objects to the workspace and prohibiting them from being sweeped off
the workspace, and thus adding to the difficulty of the task challenging.

@@

The control examples were scaled between 1 and -1 for each dimension independently. To be robust to lighting and reduce the dimensionality of the problem, we applied a binary mask to each channel of the 250x250 RGB image, the mask would set to 1 values above 125 and 0 other wise.  We then validated that all information (i.e. location of the gripper, cluttered shapes and goal object) where still visible in the masked image.
The policy $\pi_\theta$ outputs delta position control signals for a given input video frame.
Originally we considered also controlling two additional degrees of freedom of the arm: a turn-table motor controlling
the rotation of the disc workspace and the single degree of freedom of the robot gripper. However, in initial
experiments controlling the turn table proved unintuitive and was rarely used and the gripper degree of freedom was only used at the end of a policy.
As a result, we labelled to set these output degrees of freedom with zero and instead automatically closed the gripper
at the final T=100 timestep. The joint controls were limited to $\pm 15$ degrees for rotation and $1$ cm for the
extension degree of freedom.

To determine our network architecture we preformed a search over {\color{blue} FP: how many?} different architectures trained after 400 iterations with a batch size of 200. The set of architectures consist of different network architectures as well as different momentum
terms { \color{blue} FP: what? details}, and weight initialization schemes. We trained all networks on a dataset of 6K images labeled with the Analytical Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.

To test the performance of a policy, we created a test set composed of 20 different configurations each containing
objects that were not in the training set.  The test set configurations varied in the number of objects on the table
{\color{blue} FP: how many?}, size of objects and relative pose of each object. The training objects and the novel
objects introduced during testing are shown in Fig. \ref{fig:shape_set}.  We measure success by weather the object was
in the gripper at the final timestep. Examples are displayed in Fig. \ref{fig:suc_meas}. 
Per iteration of DAgger we roll out 20 trajectories which corresponds to 2000 video frame images.
Thus 100 robotic trials correspond to 5 iterations of DAgger.

@@

\caption{ \footnotesize The performance and cost of each policy trained with a supervisor is reported. The bar graphs
shows the breakdown in terms of situations the policy encountered on the test set. The top row corresponds to policies
only trained with one supervisor: AS, Crowdsourced or Human Expert. The bottom corresponds to policies trained with a
hierarchy of supervisors: AS and Crowdsource, AS and Human Expert, AS, Crowdsourced and Human Expert. The final bottom right plot demonstrates the full hierarchy, which achieves the best performance (0.8).  (WILL CLEAN UP ONCE WE DESCRIBE SCORE)  }

@@

We first test that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain
similar performance . We compare having only a AS Supervisor for a fixed amount of data to having only an Human Expert,
and to having the hierarchy of both . The non-hierarchical policies trained with the human expert supervisor only for
160 demonstrations or only the AS supervisor for 160 demonstrations.  The policy trained with a hierarchical supervisor
first receives  100 demonstrations from the AS supervisor and  60 demonstrations from the expert supervisor.

Our results, shown in Fig. \ref{fig:perf_results}, are the policy trained with just the AS supervisor achieves a score of $0.325\%$, the policy trained with just an expert achieves $0.54\%$ and the policy trained with a hierarchy of supervisor achieves $0.55\%$.  Thus, the hierarchical supervisor and expert supervisor achieve approximately the same performance. However,training with a hierarchical supervisor yields a $40\%$ reduction in cost incurred compared to the policy trained with only an expert supervisor.

@@

@@

\caption{\footnotesize The performance of each policy trained with a different data management strategy is reported. The
bar graphs shows the breakdown in terms of situations the policy encountered on the test set. Each policy was trained
with the AS to Human Expert hierarchical supervisor. From left to right is the following data management strategies: Dataset Aggregation, Weight Transfer and Regularization. Regularization achieves the highest performing score of (0.18) }
\label{fig:cost_result}
\end{figure}

Our results, shown in Fig. \ref{fig:perf_results}, indicate that the policy trained with just the crowdsourced supervisor achieves
a score of $41\%$. The policy trained with the hierarchical crowdsourced and algorithmic supervisor receives $43\%$ on our test set compared to $55\%$ with the motion planning and expert supervisors hierarchy. The total cost received with the only crowdsource supervisor was 15, while the hierarchical supervisor was 7.

\begin{figure}[t]
\includegraphics{f_figs/big_data.eps}
\centering 
\caption{ \footnotesize The performance and cost of right the full hierarchy, which achieves the best performance (0.8). The bar graphs shows the breakdown in terms of situations the policy encountered on the test set.  (WILL CLEAN UP ONCE WE DESCRIBE SCORE)   }
\vspace*{-20pt}
\label{fig:big_data}
\end{figure}

We compare each strategy on a hierarchy of an algorithmic supervisor trained with 100 iterations and then advancing to a human expert supervisor trained with 60 iterations.  Our results reported in Fig.\ref{fig:cost_result}, show that aggregation strategy achieves $0.18\%$, the weight transfer strategy achieves $0.55\%$ and the regularized stochastic gradient update strategy achieves $0.63\%$. Thus, suggesting that techniques to help the policy remain close to the previously trained supervisor are useful for effectively switching between supervisors.

We are thus interested in not storing the dataset collected from the previous supervisor and only remembering the
current $\theta_{m,K}$ weight parameters. Thus, we propose only performing DAgger for each individual supervisor in the
hierarchy and using the resulting weight vector to bootstrap the learning of the next supervisor. We found empirically
in Sec. \ref{sec:Exp} that it is also beneficial to add the new dataset the states and controls applied by the current
policy $\pi_{\theta_{m,k}}$ that the current supervisor agreed with by some euclidean distance
$\tilde{\epsilon}$ {\color{blue}FP:what epsilon?}. Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.

\subsection{Scaling the Hierarchy}
The final experiment we ran is to run our algorithm on a hierarchy with 3 supervisors: AS, crowdsourced and human
expert. We ran each policy until we observed the pay out in terms of reward achieved was not increasing. This results in
AS for 100 demonstrations, crowdsourced for 120 demonstrations and human expert for 100 demonstrations. Thus resulting in 320 trials on the robot and approximately 210,000 annotated images of what control the robot should apply. Note there is less images that total states visited because the human supervisors only labeled when confident in their decisions.

The results of our trained policy, as shown in Fig. \ref{fig:big_data}, demonstrate that by leveraging a hierarchy we are able to achieve a score of $80\%$ with a cost of only 113. We note that policy trained with the human expert supervisor, which incurred a cost of $160$, was only able to achieve a score of $0.66\%$.

While our policy was able to do substantially better, it did score a near successful  $40\%$. These failure modes where do to the robot not being able to accurately manipulate smaller objects, where slight perturbations could result them being pushed into the gripper, and accurately controlling the goal object to land in the circle (i.e. sometimes pushing against the side of the circle instead). We attribute this problem to a limit in the detail of precision our supervisors can currently give, future work will look at more precise analytical methods and fine tuning the policies via self-learning.

\subsection{Discussion of Failure Modes}
{\color{blue} FP: Michael, please add a 3x3 figure of "hard" examples and discuss failure modes.}

@@

>>>>

\begin{abstract}
For applications such as Amazon warehouse order fulfillment, robots must grasp a desired object amid clutter: other objects that block direct access.  This can be difficult to program explicitly due to uncertainty in friction and push mechanics and the large number of objects that can be encountered. Online Learning from Demonstration (LfD) algorithms such as DAgger and SHIV have potential to learn robot control policies for tasks where the system dynamics and the cost function are unknown. To reduce the burden on human experts to provide control demonstrations, we propose using a hierarchy of supervisors and a Deep Learning network to learn a grasping in clutter task.  We consider 3 levels of supervisor, a fast motion planner that ignores obstacles, crowdsourced human workers who
provide appropriate robot control values via online videos, and local human experts.  Experiments suggest that we can leverage a hiearchy of supervisors to obtain 22,000 examples and achieve 80\% success on a held out test set of unknown objects.

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{f_figs/teaser.eps}
\caption{
Three roll-outs on a Zymark 3-DOF Robot of a fully trained grasping in clutter policy (one per column, top to bottom) which was trained using a
hierarchy of three supervisors consisting of an analytical motion planning, crowd-sourcing and human expert. 
Red shapes indicate clutter objects and the robot is trained to reach the yellow circle. The trained manipulation policy is represented as a deep neural network that recieves as input an image of the scene and outputs a change in state position. The resulting policy learns to sweep away clutter objects and reach the goal object. }
\vspace*{-20pt}
\label{fig:teaser}
\end{figure}

@@

\section{Robot Grasping in Clutter}
Let us now describe how we apply the above approach for the grasping in clutter problem. We consider a robot grasping an
object in a cluttered environment. The robot's goal is to grasp a yellow cylindrical target object while other extruded
planar objects obstruct the path towards the goal object. Since contact dynamics are difficult to model \cite{kitaevphysics,kingnonprehensile}, we do not assume the knowledge of explicit object or dynamics models and instead learn a grasping policy directly from labeled
overhead video data. The state space space $\mathcal{X}$, is hence given by an image from an overhead video
camera, observing a set of K objects, the robot arm and a goal object in a bounded workspace. As the underlying reward
function, or $r: \mathcal{X}\times \mathcal{U} \rightarrow \lbrace 0, 1\rbrace$, where $U$ denotes continuous control
signals given by delta values of joint angles. We consider the following three supervisors $S_1, S_2, S_3$.

\noindent \textbf{Algorithmic Supervisor} Our first supervisor, $S_1$, is a first order motion planner that that computes
control signals for the robot to reach the goal object in a straight line, ignoring the presence of obstacles. Our
method employs template matching to identify the goal object in the image and uses the forward dynamics of the robot to
computes the relative change in direction the robot should apply as a control. The template matching is implemented in
OpenCV and uses the normalized cross-correlation filter~\cite{opencv_library}. This supervisor is intentionally
simplistic to execute and implement, and is designed to just provide an initial improvement of a random neural network policy.
We assign a cost of $C_1 = \$0.01$ to this supervisor, which stems from the amtorized cost need to implement this supervisor. 
\begin{figure}[t]
\centering

@@

\noindent \textbf{CrowdSourced Supervisor} The second supervisor, $S_2$, relies on a crowd source service, called Amazon
Mechanical Turk (AMT). The AMT platform makes readily available thousands of human workers that we can query to provide robot
supervision examples for approximately \$0.1 per robot trial. 
We designed the supervision interface shown in Fig. \ref{fig:overlays}. The interface displays a video of a roll-out of
the current robot policy and allows the human supervisors to command an overlay visualization of the robot arm to
showcase a deviation to the current policy that should be applied with a maximal angle joint deviation of 15 degree and maximal extension deviation of 1cm  to
the current roll-out.

@@

\section{Experiments} \label{sec:Exp}

\begin{figure}[t]
\centering

\includegraphics{f_figs/binary_segment.eps}

\caption{\footnotesize Example of how the binary mask applied to each RGB channel affects the input data. As you can see it reduces the dimensionality of each channel's pixel value from the range of [0,255] to [0,1], which can allow for less data needed during learning and robustness to small lighting conditions.  }

\label{fig:b_seg}
\end{figure}

\begin{figure}[t]
\centering

@@

\caption{\footnotesize  On the right is examples of training configurations we presented to the robot. The shapes were arranged around the goal object in different poses and in different parts of the workspace. At testing time, we had similar configurations but some shapes were unknown objects that were not trained on. }
\vspace*{-20pt}
\label{fig:suc_meas}
\end{figure}

@@

\subsection{Experimental Setup}
We work with a Zymark robot to perform a grasping in clutter task. The robot, shown in Fig. \ref{fig:robot}, has a 3 dimensional internal state of base rotation, arm extension and gripper. The robot is commanded via state position requests, which are tracked by a tuned PID controller. We used
relative state control because this enabled us to easily enforce stay out zones (such as where a human operator might
be) and to register control signals to the labeling interface in Fig. \ref{fig:overlays}. We utilize the two main rotational joints of the
robot as degrees of freedom which are controled by a neural network policy $\pi_{\theta}$ trained on image data taken by
an overhead Logitech C270 camera. Examples of images from the camera can be seen in Fig. \ref{fig:teaser}.

We consider objects made of Medium Density Fiberboard with an average 4" diameter. The objects used to form clutter are
painted red while the goal object is a yellow cylinder. The robot workspace consists of a disk region which is
surrounded by an elevated plate constraining the objects to the workspace and prohibiting them from being sweeped off
the workspace, and thus adding to the difficulty of the task challenging.

@@

The control examples were scaled between 1 and -1 for each dimension independently. To be robust to lighting and reduce the dimensionality of the problem, we applied a binary mask to each channel of the 250x250 RGB image, the mask would set to 1 values above 125 and 0 other wise, each channel is shown in Fig. \ref{fig:b_seg}.
The policy $\pi_\theta$ outputs delta position control signals for a given input video frame.
Originally we considered also controlling two additional degrees of freedom of the arm: a turn-table motor controlling
the rotation of the disc workspace and the single degree of freedom of the robot gripper. However, in initial
experiments controlling the turn table proved unintuitive and was rarely used and the gripper degree of freedom was only used at the end of a policy.
As a result, we labeled to set these output degrees of freedom with zero and instead automatically closed the gripper
at the final T=100 timestep. The joint controls were limited to $\pm 15$ degrees for rotation and $1$ cm for the
extension degree of freedom.

To determine our network architecture we preformed a search over 40 different architectures trained after 400 iterations with a batch size of 200  The set of architectures consisted of different network architectures in terms of convolutional layers, fully connected layers and size of each one as well as different gradient descent momentum
terms used in learning, and weight initialization schemes. In finding an architecture, we trained all networks on a dataset of 6K images labeled with the Algorithmic Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.

To test the performance of a policy, we created a test set composed of 20 different configurations each containing
objects that were not in the training set.  The training objects and test
objects introduced during testing are shown in Fig. \ref{fig:shape_set}. The test set configurations varied by placing unknown objects from Fig. \ref{fig:shape_set} in addition to the object trained on. Examples of training and test configurations are shown in Fig. \ref{fig:suc_meas}.  We measure success by whether the object was
in the gripper at the final timestep. 
Per iteration of DAgger we roll out 20 trajectories which corresponds to 2000 video frame images. Thus 100 robotic trials correspond to 5 iterations of DAgger.

@@

\caption{ \footnotesize The Score (or \% Succesful) and cost of each policy trained with a supervisor is reported. The bar graphs
shows how many successful and failed situations occurred. The top row corresponds to the experiments on hierarchical supervisors: Algorithmic, Human Expert and the hierarchy of Algorithmic to Human Expert. 
 The bottom corresponds to experiments on testing a crowdsourced supervisor: Crowdsourced and the hierarchy Algorithmic and Crowdsourced, AS and Human Expert, AS, Crowdsourced and Human Expert.   }

@@

We first test that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain
similar performance . We compare having only a Algorithmic Supervisor for a fixed amount of data to having only an Human Expert,
and to having the hierarchy of both . The non-hierarchical policies trained with the human expert supervisor only for
160 demonstrations or only the AS supervisor for 160 demonstrations.  The policy trained with a hierarchical supervisor
first receives  100 demonstrations from the AS supervisor and  60 demonstrations from the expert supervisor.

Our results, shown in Fig. \ref{fig:perf_results}, are the policy trained with just the Algorithmic Supervisor achieves a score of $30\%$, the policy trained with just the Human Expert Supervisor achieves $55\%$ and the policy trained with a hierarchy of supervisor achieves $60\%$.  Thus, the hierarchical supervisor and expert supervisor achieve approximately the same performance. However,training with a hierarchical supervisor yields a $40\%$ reduction in cost incurred compared to the policy trained with only an expert supervisor.

@@

Our results, shown in Fig. \ref{fig:perf_results}, indicate that the policy trained with just the crowdsourced supervisor achieves
a score of $35\%$. The policy trained with the hierarchical crowdsourced and algorithmic supervisor receives $45\%$ on our test set compared to $60\%$ with the motion planning and expert supervisors hierarchy. The total cost received with the only crowdsource supervisor was 15, while the hierarchical supervisor was 7.

We compare each strategy on a hierarchy of an algorithmic supervisor trained with 100 iterations and then advancing to a human expert supervisor trained with 60 iterations.  Our results reported in Fig.\ref{fig:cost_result}, show that aggregation strategy achieves $15\%$, the weight transfer strategy achieves $55\%$ and the regularized stochastic gradient update strategy achieves $65\%$. Thus, suggesting that techniques to help the policy remain close to the previously trained supervisor are useful for effectively switching between supervisors.

We are thus interested in not storing the dataset collected from the previous supervisor and only remembering the
current $\theta_{m,K}$ weight parameters. Thus, we propose only performing DAgger for each individual supervisor in the
hierarchy and using the resulting weight vector to bootstrap the learning of the next supervisor. We found empirically
in Sec. \ref{sec:Exp} that it is also beneficial to add the new dataset the states and controls applied by the current
policy $\pi_{\theta_{m,k}}$ that the current supervisor agreed with by some euclidean distance
$\tilde{\epsilon} = 0.01$. Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.

\begin{figure}[t]
\includegraphics{f_figs/big_data.eps}
\centering 
\caption{ \footnotesize  The performance and cost of the policy trained on the full hierarchy with of Algorithmic, Crowdsourced and Human Expert. The policy achieves a success rate or score of $80\%$ success. The total cost though after 320 trials is only 113.  }
\vspace*{-20pt}
\label{fig:big_data}
\end{figure}

\subsection{Scaling the Hierarchy}
The final experiment we ran is to run our algorithm on a hierarchy with 3 supervisors: AS, crowdsourced and human
expert. We ran each policy until we observed the pay out in terms of reward achieved was not increasing. This results in
AS for 100 demonstrations, crowdsourced for 120 demonstrations and human expert for 100 demonstrations. Thus resulting in 320 trials on the robot and approximately 22,000 annotated images of what control the robot should apply. Note there is less images that total states visited because the human supervisors only labeled when confident in their decisions.

The results of our trained policy, as shown in Fig. \ref{fig:big_data}, demonstrate that by leveraging a hierarchy we are able to achieve a score of $80\%$ with a cost of only 113. We note that policy trained with the human expert supervisor, which incurred a cost of $160$, was only able to achieve a score of $55\%$.

The behavior of the learned policy appears to find gaps in between the clutter objects and sweeps left to right,  until the objects are pushed apart and then moves towards the goal object, as illustrated in Fig. \ref{fig:teaser}. We noticed the amount of sweeping is proportional to the size of the gap in the between the cluttered objects. Small gaps tend to cause a high frequency of sweeping versus large gaps in which the robot may only push the objects away in one sweep.

While our policy was able to do  better with the full hierarchy. There still persists some failure modes in our test configurations are shown in Fig. \ref{fig:failure_modes}. The cause of the failure modes are either the robot sweeps to far and jams the objects against the inscribed circle around the workspace or  an obstacle object falls into the gripper while being pushed. Furthermore, it is unclear how well these results will generalize to configurations that are not cluttered objects placed around the goal object.

\begin{figure}[t]
\centering 
\includegraphics{f_figs/failure_modes.eps}

\caption{\footnotesize The four failure modes in our test set on the fully trained policy. On the left the robot sweeps to far and the collision objects jam up against the edge of the work space. On the right, both the banana and the boot are prone to get entrapped in the gripper during pushing and prevent the gripper from reaching the circle.  }
\label{fig:failure_modes}
\end{figure}

@@

\caption{\footnotesize The performance of each policy trained with a different data management strategy is reported. The
bar graphs shows the breakdown in terms of situations the policy encountered on the test set. Each policy was trained
with the AS to Human Expert hierarchical supervisor. From left to right is the following data management strategies: Dataset Aggregation, Weight Transfer and Regularization. Regularization achieves the highest performing score of (0.65) }
\label{fig:cost_result}
\end{figure}

@@

Further information, video and code can be found at the following \url{http://berkeleyautomation.github.io/HierSupCASE/}.
